---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pokedex

<!-- badges: start -->
<!-- badges: end -->

The `pokedex` package provides an R interface to search through the [pokedex_data] for names of Pokemon that have a specific Type. You can also display the official image of a Pokemon you would like to look up.

## Installation

You can install the development version of the `pokedex` package from [GitHub](https://github.com/) with:

``` r
# install.packages("pokedex")
devtools::install_github("RISAW1130/pokedex")
```

## Usage

Given a specific Type name as an input, the `pokemon_search()` function returns a list object containing names of Pokemon that has the specified Type as its Type 1 variable.

```{r example}
library(pokedex)
```

Given a specific name of a Pokemon, the `pokemon_photo()` function displays the corresponding official PNG image of the specified Pokemon in the R plot window:

```{r}
pokemon_photo("Pikachu")
```
