---
title: "Using the pokedex package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the pokedex package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Browsing Pokedex Function

The main function of the pokedex package is to let you browse pokedex from within R. Let's see how we can accomplish this. First, load the `pokedex` package.

```{r setup}
library(pokedex)
```

## Searching Pokemon Names by Type

Then, use the `search_pokedex()` function to to search for Pokémon based on their primary type (`Type1`), using a case-insensitive match.

```{r}
fire_pokemon <- search_pokedex(type1 = "Fire")
print(fire_pokemon)
```

## Plotting Pokemon Picture (PNG)

The `pokemon_photo` function displays the actual and specified Pokemon image in the plot window:

```{r}
pokemon_photo("Pikachu")
```

## Pokemon Data 
The pokedex package also comes with a built-in dataset containing information on 1,010 Pokémon, including those from the 1st through 9th generations.
```{r}
pokedex::pokedex_data
```
